%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Aryan Dalal} \\ \vspace{1pt}
     \href{https://wa.me/8652207970}
    {\small \raisebox{-0.1\height}\faPhone\ +91-8652207970} ~ \href{mailto:aryan.d.dalal@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{aryan.d.dalal@gmail.com}} ~ 
    \href{https://aryan-dalal.vercel.app/}{\raisebox{-0.2\height}\faLink\  \underline{Website}} ~ 
    \href{https://www.linkedin.com/in/aryan-d-dalal/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}}  ~
    \href{https://github.com/spicybeanos}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/spicybeanos}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manipal Institute of Technology}{Aug. 2022 – May 2026}
      {B-Tech in Computer Science and Engineering}{Bengaluru, KA}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Nuvama wealth }{June 2024  -- July 2024 }
      {Application Developer Intern }{Mumbai, MH}
      \resumeItemListStart
        \resumeItem{Built a DotNET script to fetch data from a paid third-party API and cache it locally to avoid repeated expensive calls.}
        \resumeItem{Cleaned and formatted inconsistent API responses, storing them in structured files for efficient access.}
      \resumeItemListEnd

    \resumeSubheading
      {Tech Solstice Tech-fest}{Feb 2025 -- April 2025}
      {Technical Head}{Bengaluru, KA}
      \resumeItemListStart
      \resumeItem{Lead development of an engaging, cyberpunk-themed website and Android app for the fest using SvelteKit and React Native.}
      \resumeItem{Managed a team of 5 devs using GitHub for version control, task delegation, and rapid iteration.}
        \resumeItem{Integrated Supabase for user/event management and Google Login API for secure authentication.}
        \resumeItem{Deployed via Vercel, collaborated with designers, and ensured real-time control panel for dynamic updates.}
    \resumeItemListEnd

    \resumeSubheading
      {BizDateUp }{June 2024  -- August 2024 }
      {Fullstack Intern }{Mumbai, MH}
      \resumeItemListStart
        \resumeItem{Built a KPI Management System using React, Express, Supabase, PostgreSQL, and Prisma, enabling HR to define KPIs, employees to report progress, and managers to conduct performance reviews and appraisals.}
        \resumeItem{Developed a dashboard with interactive graphs (bar, line, pie) to visualize team performance across timeframes, aiding data-driven decision-making.}
        \resumeItem{Created a compliance tracking app with React + TypeScript and FastAPI to monitor and audit the buying, selling, and issuance of securities for regulatory compliance.}
        \resumeItem{Implemented role-based access, JWT authentication, and scalable backend APIs to ensure secure, modular, and maintainable systems across platforms.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/spicybeanos/mitb-solstice-2025-frontend}{\textbf{Solstice Website}}} $|$ \emph{Svelte, SvelteKit, typescript, Node.js, javascript, Supabase, Vercel}}{Feb 2025}
          \resumeItemListStart
            \resumeItem{Developed the one-stop eye-catching cyberpunk website for my college's annual tech fest, responsible for handling requests and data for over ten thousand users.}
            \resumeItem{Website handles event registrations, pass purchases, advertisements of talk and workshops as well as a ticket system to solve custom user requests and queries, eliminating the need of a physical desk to solve queries.}
            \resumeItem{Website included a control panel for organizers to change content on the website, eliminating any IT intervention.}
            \resumeItem{Assigned a static QR (which can be screenshot and kept) to each user that register to streamline and speed up user verification by scanning the QR on the solstice verifier app instead of manual typing.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/spicybeanos/solstice-verifier-app}{\textbf{Solstice verifier app}}} $|$ \emph{React-native, Expo, TSX}}{April 2025}
          \resumeItemListStart
            \resumeItem{Created an Android application using expo react-native to quickly get user info including the pass purchase}
            \resumeItem{Utilized expo react-native and the expo camera to quickly scan QR codes and check with the website about the user's status, cutting down event entry processing time by 65\%.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{\href{https://github.com/spicybeanos/badger-script}{\textbf{Compiler for custom language badger-script in rust}}} $|$ \emph{Rust, Cargo}}{March 2025}
          \resumeItemListStart
            \resumeItem{Designed a compiler made in the rust programming language for a custom programming language called badger-script}
            \resumeItem{Compiled to custom byte code to allow execution to any platform, proccessor and operating system}
            \resumeItem{Implemented an interpreter to run the badger-scripts}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Rust, Java, C, HTML/CSS, JavaScript, TypeScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform} \\
     \textbf{Technologies/Frameworks}{: GitHub, SupaBase, Vercel, React, React-native, Svelte, SvelteKit, Nextjs, ExpressJs, NodeJs, Prisma, Axios} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Codex}{Aug 2022 - Aug 2023}{Game Development Head}{MIT Bengaluru}
            \resumeItemListStart
                \resumeItem{Led and managed three independent game development teams, overseeing project timelines, providing technical and creative guidance, and ensuring successful completion of each team's game project under my supervision.}
                \resumeItem{Held tutorials about game development in unity and 3D modeling in blender.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
